Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-03 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
intro

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{helvet,times,courier}
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{cite}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{caption} 
\captionsetup[table]{skip=10pt}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A decomposition based on constrained clustering algorithms for JSP\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958} \and
Martin Gebser\inst{1,2}\orcidID{0000--0000-0000-0000}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, konstantin.schekotihin and martin.gebser\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Scheduling is a crucial problem appearing in various domains, such as manufacturing, transportation, or healthcare. In most problem definitions, the goal is to schedule a given set of operations on available resources to complete the operations as early as possible. Unfortunately, most scheduling problems cannot be solved efficiently. Therefore, the research of suitable approximation methods is of primary importance.

@@

\keywords{Job-shop Scheduling  Problem \and Constrained Clustering \and Time Windows \and Answer Set Programming.}
\end{abstract}
%
%
%
\section{Introduction}
Nowadays, the massive progress and development of the internet and online technologies, data generated by machines and devices, product development, quality and inventory management systems, or production planning systems has become huge and is expected to increase in the coming years. Hence, to capture long-term revenues and sustainable competitive advantages, companies must manage the knowledge and have the valuable information to make the right decision at the right time \cite{benabdellah2019survey}. \\

It can be assumed that knowledge management is a crucial issue in the industry. To extract implicit, unknown, and potentially useful information from data, we use data mining techniques that have been responsible for many of artificial intelligence’s recent successes. 
Clustering is one of these techniques, which is applied whenever the extracted data is not labeled, i.e., the semantics of this data is with respect to the application is unclear. Therefore, clustering has always been an exploratory but critical task in the knowledge discovery process, with applications ranging from image processing, production systems, and information retrieval \cite{benabdellah2019survey}. Clustering is a technique that aims to partition a dataset (objects) into subsets by identifying similar objects and aggregating them in the same cluster while the dissimilar objects should belong to different clusters.\\

The data sets could be composed entirely of either numeric features or symbolic features. For the numeric feature, we will use the Euclidean distance metric. However, for symbolic features, the Hamming distance is computed. Since our problem contains only numeric features, we will use Euclidean distance to determine the distance between the objects \cite{aloise2009np, wagstaff2001constrained,macqueen1967some}.\\
%\comment{The next paragraph jumps to a distance, which is one of the similarity measures in the Euclidean space. One should explain this transition.}

Furthermore, from an optimization perspective, the main objective is to minimize the distance between objects falling in the same cluster and maximize the distance between the others that belong to different clusters. Since clustering does not use a subset of the dataset as labels to learn a classification model, clustering differs from classification \cite{wagstaff2001constrained}. In other words, with the terminology of machine learning, clustering is a form of an unsupervised task, which calculates the similarity between data objects without knowing the proper attribution~\cite{li2018geometric}. Due to these unsupervised characteristics, clustering is known as one of the most challenging machine learning tasks \cite{benabdellah2019survey}. \\

Clustering has been widely applied in several disciplines; one is production-planning systems~\cite{nananukul2013clustering,koskosidis1992clustering}, more specifically scheduling \cite{yashar2013multi,tong2016research}. 
%\comment{Are there any citations for the claim above?}
Scheduling is one of the most complex problems in the industry. Scheduling of operations involves resource allocation over a period of time to perform a series of tasks, where one of the most critical problems is the Job-shop Scheduling Problem (JSP). The JSP has been known as a complex and combinatorial optimization problem, and it has been proven to be NP-hard \cite{baker1974introduction,lenstra1979computational}. Therefore, it is very difficult to reach an optimal solution in a reasonable time, even for small instances. However, from a practical perspective, the JSP scale is large, where the number of operations can be up to 10,000s in some workshops \cite{zhang2010hybrid}. \\

This work intends to apply the clustering techniques to decompose the problem into sub-problems, where the number of clusters corresponds to the number of sub-problems (windows), and the operations correspond to data objects. For the JSP, an instance consists of a set of jobs to be processed on machines. The number of jobs is $n$, and the number of machines is $m$. Each job contains $m$ operations with the operation precedence constraints. Each operation should be executed on machine $m$ for a certain amount of time. Since the problem at hand has precedence constraints, it is required to apply a constrained clustering approach for the decomposition \cite{wagstaff2001constrained}. Although many studies proposed different constrained clustering methods in \cite{zhang2019framework,wagstaff2001constrained,ding2020unified}. However, most of those checked whether two data objects must be assigned into the same cluster. For the JSP, it is essential to consider the sequencing between the clusters to handle the precedence constraints. More specifically, our proposed method will not permit to assign an operation into a particular cluster if the predecessor of that operation is not yet assigned to the same or previous cluster(s). \\

@@

\begin{table}[h!]
\fontsize{12}{9}
\setlength{\tabcolsep}{10.0pt}
\centering
  \begin{center}
    \caption{An example of a Job-shop Scheduling Problem.}
    \label{tab1}
 %\begin{adjustwidth}{0.0cm}{}
    \begin{tabular}{c c c}
      \textbf{Operation} & \textbf{Machine} & \textbf{Procession Time} \\
      \hline
								\\
      $O_{1,1}$  & 2  &  9  	\\
      $O_{1,2}$  & 3  &  3  	\\
      $O_{1,3}$  & 1  &  5  	\\
								\\
      $O_{2,1}$  & 3  & 4  	\\
      $O_{2,2}$  & 2  & 6  	\\
      $O_{2,3}$  & 1  & 2  	\\
								\\
      $O_{3,1}$  & 1  & 4  	\\
      $O_{3,2}$  & 3  & 3  	\\
      $O_{3,3}$  & 2  & 5  	\\
    \end{tabular}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{helvet,times,courier}
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{cite}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{caption}
\usepackage{todonotes}
\captionsetup[table]{skip=10pt}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Decomposition-based Job-shop Scheduling with Constrained Clustering}%\thanks{Supported by organization x.}}
%
\titlerunning{Decomposition-based JSP with Constrained Clustering}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958} \and
Martin Gebser\inst{1,2}\orcidID{0000--0000-0000-0000}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, konstantin.schekotihin and martin.gebser\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Scheduling is a crucial problem appearing in various domains, such as manufacturing, transportation, or healthcare. In most problem definitions, the goal is to schedule a given set of operations on available resources to complete the operations as early as possible. Unfortunately, most scheduling problems cannot be solved efficiently. Therefore, the research of suitable approximation methods is of primary importance.

@@

\keywords{Job-shop Scheduling  Problem \and Constrained Clustering \and Time Windows \and Answer Set Programming.}
\end{abstract}
%
%
%
\section{Introduction}
Scheduling is one of the most crucial problems in various industrial, transportation, or healthcare applications. 
\todo{add 1-2 citations for each application} 
These applications resulted in different definitions of scheduling problems, with Job-shop Scheduling Problem (JSP) being among the most popular ones.
In JSP, operations of given jobs must be scheduled on available machines in an optimal way wrt.\ some pre-defined criteria. The latter include, for instance, minimization of makespan, i.e., the completion time of the last job, or tardiness, i.e., the sum of delays for all jobs completed after their deadlines.

However, JSP is a NP-complete combinatorial optimization problem \cite{DBLP:journals/mor/GareyJS76,SOTSKOV1995237} for which no efficient algorithms are known. Therefore, searching for an optimal solution with modern approaches like Answer Set Programming (ASP), Mixed Integer Programming, or Constraint Programming \todo{cite at least 1 paper solving JSP with these methods} often takes too much computation time, even for small instances. Practical applications require solving JSP instances of vast scale with thousands of operations \cite{zhang2010hybrid}.
As a result, many researchers focused on the development of efficient algorithms for finding high-quality approximations of the optimal schedule, including dispatching rules and other heuristic approaches~\cite{blackstone1982state}, or stochastic optimization techniques \cite{DBLP:journals/informs/VaessensAL96,DBLP:journals/jim/CalisB15}.  
The main issue of these approaches is that they require manual parametrization for a particular scheduling problem, which is tedious and error-prone. For instance, heuristic approaches might require the development of new heuristics or their combinations. Similarly, default parameters of stochastic methods might result in a finding of mediocre schedules.    
As a result, much focus of the recent research lies on the automation of the parametrization using machine learning techniques~\cite{bengio2020machine}.

%Nowadays, the massive progress and development of the internet and online technologies, data generated by machines and devices, product development, quality and inventory management systems, or production planning systems has become huge and is expected to increase in the coming years. Hence, to capture long-term revenues and sustainable competitive advantages, companies must manage the knowledge and have the valuable information to make the right decision at the right time \cite{benabdellah2019survey}. \\

%It can be assumed that knowledge management is a crucial issue in the industry. To extract implicit, unknown, and potentially useful information from data, we use data mining techniques that have been responsible for many of artificial intelligence’s recent successes. 
%Clustering is one of these techniques, which is applied whenever the extracted data is not labeled, i.e., the semantics of this data is with respect to the application is unclear. Therefore, clustering has always been an exploratory but critical task in the knowledge discovery process, with applications ranging from image processing, production systems, and information retrieval \cite{benabdellah2019survey}. Clustering is a technique that aims to partition a dataset (objects) into subsets by identifying similar objects and aggregating them in the same cluster while the dissimilar objects should belong to different clusters.\\

%The data sets could be composed entirely of either numeric features or symbolic features. For the numeric feature, we will use the Euclidean distance metric. However, for symbolic features, the Hamming distance is computed. Since our problem contains only numeric features, we will use Euclidean distance to determine the distance between the objects \cite{aloise2009np, wagstaff2001constrained,macqueen1967some}.\\
%\comment{The next paragraph jumps to a distance, which is one of the similarity measures in the Euclidean space. One should explain this transition.}

%Furthermore, from an optimization perspective, the main objective is to minimize the distance between objects falling in the same cluster and maximize the distance between the others that belong to different clusters. Since clustering does not use a subset of the dataset as labels to learn a classification model, clustering differs from classification \cite{wagstaff2001constrained}. In other words, with the terminology of machine learning, clustering is a form of an unsupervised task, which calculates the similarity between data objects without knowing the proper attribution~\cite{li2018geometric}. Due to these unsupervised characteristics, clustering is known as one of the most challenging machine learning tasks \cite{benabdellah2019survey}. \\

%Clustering has been widely applied in several disciplines; one is production-planning systems~\cite{nananukul2013clustering,koskosidis1992clustering}, more specifically scheduling \cite{yashar2013multi,tong2016research}. 
%\comment{Are there any citations for the claim above?}

In this work, we suggest a clustering-based method that automatically decomposes a JSP instance into sub-instances which can be tackled by 
optimization algorithms of an ASP solver. 
General clustering algorithms are unsupervised learning methods that partition a given set of objects into disjoint clusters, where each cluster comprises closest objects wrt.\ some distance function. 
In scheduling settings, however, clusters must satisfy additional constraints, which define precedence relations between operations of a job. Standard constrained clustering algorithms are not applicable in scheduling scenarios since they usually allow for the definition of disjointness constraints, which specify objects that cannot appear in one cluster \cite{zhang2019framework,wagstaff2001constrained,ding2020unified}. 
%\cite{wagstaff2001constrained}
%where the number of clusters corresponds to the number of sub-problems (windows), and the operations correspond to data objects. For the JSP, an instance consists of a set of jobs to be processed on machines. 
%The number of jobs is $n$, and the number of machines is $m$. Each job contains $m$ operations with the operation precedence constraints. Each operation should be executed on machine $m$ for a certain amount of time. Since the problem at hand has precedence constraints, it is required to apply a constrained clustering approach for the decomposition \cite{wagstaff2001constrained}. Although many studies proposed different constrained clustering methods in \cite{zhang2019framework,wagstaff2001constrained,ding2020unified}. However, most of those checked whether two data objects must be assigned into the same cluster. 
Therefore, our clustering method implements a novel type of constraints, which prevent the assignment of an operation to a cluster if its preceding operation is not yet assigned to the same or previous cluster.

@@

\begin{table}[h!]
%\fontsize{12}{9}
\setlength{\tabcolsep}{10.0pt}
\centering
  \begin{center}
    \caption{An example of a Job-shop Scheduling Problem.}
    \label{tab1}
 %\begin{adjustwidth}{0.0cm}{}
    \begin{tabular}{c c c}
      \textbf{Operation} & \textbf{Machine} & \textbf{Procesing Time} \\
      \hline
								\\
      $O_{1,1}$  & 2  &  9  	\\
      $O_{1,2}$  & 3  &  3  	\\
      $O_{1,3}$  & 1  &  5  	\\
								\\
      $O_{2,1}$  & 3  & 4  	\\
      $O_{2,2}$  & 2  & 6  	\\
      $O_{2,3}$  & 1  & 2  	\\
								\\
      $O_{3,1}$  & 1  & 4  	\\
      $O_{3,2}$  & 3  & 3  	\\
      $O_{3,3}$  & 2  & 5  	\\
    \end{tabular}
